Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-24 Paper/Paper.tex
more comments and tweaks to sections 4 and 5

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{code_variance}
\end{center}
\caption{\small{Average variance in time of a codebook. The vertical
axis cuts at the $63$rd pattern, a rough estimate of the number of 
sustained note patterns.
}}
\label{fig:code_var}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.8\columnwidth]{codes_8bars}
\end{center}
\caption{\small{Sample of longer codewords spanning over $8$ bars. Codewords
selected randomly from a codebook of size $200$. As usual, we see sustained
notes, but also some long-term structures.
}}
\label{fig:codes8bars}
\end{figure}

@@

\section{Applications}\label{sec:exps2}
We have shown the basic properties of our clustering algorithm in
Section \ref{sec:experiments}. In Section \ref{sec:visu}, we showed
how to visualize the codebook and the clusters. We know move on to
show other applications that can take advantage of our clustering.
In the next two subsections, we talk about song segmentation and
artist recognition. Our algorithm was not devised for any of these tasks,
but some information contained in the centroids can be naturally used.

>>>>

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.9\columnwidth]{code_variance}
\end{center}
\caption{\small{Average variance in time of a codebook. The vertical
axis cuts at the $63$rd pattern, a rough estimate of the number of 
codewords consisting of sustained chords.
}}
\label{fig:code_var}
\end{figure}

@@

\begin{figure}[htb]
\begin{center}
\includegraphics[width=.8\columnwidth]{codes_8bars}
\end{center}
\caption{\small{Sample of longer codewords spanning over $8$ bars. Codewords
selected randomly from a codebook of size $200$. As usual, we see sustained
notes, but also some long-term structure.
FIXME: I (ronw) like the middle-left pattern, but I'm totally confused
by those in the top right and bottom row.  Are they ever used?  They
don't seem to be smoothed out at all, and are probably outliers
containing only one or two training points.
}}
\label{fig:codes8bars}
\end{figure}

@@

\section{Applications}\label{sec:exps2}
In this section we describe two other applications of the clustering
described in this paper: the song segmentation, and artist
recognition.  This demonstrates the utility of unsupervised clustering
to FIXME ... 
% Although our algorithm was not devised for any of these
% tasks, but some information contained in the centroids can be
% naturally used.
